---
title: "Korean dyads - analysis of lexical data; posterior predictive checks"
author: "Bodo"
date: "29/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The main analysis is "analysis.Rmd". This script uses the resulting models and performs posterior predictive checks.

## Prelims

Load packages:

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(brms)
```

Get the model file names:

```{r}
files <- list.files('../models/')
```

Loop through this (they are all called "this_mdl"):

```{r}
for (i in seq_along(files)) {
  load(str_c('../models/', files[i]))
  assign(files[i], this_mdl)
}
```

## Summarize all models separately

Check the task random effects:

```{r}
coef(honorific_suffixes.mdl)$Task[,,2]
coef(honorific_lexemes.mdl)$Task[,,2]
coef(case_ellipsis.mdl)$Task[,,2]
coef(pronouns.mdl)$Task[,,2]
coef(ideophones.mdl)$Task[,,2]
coef(backchannels.mdl)$Task[,,2]
coef(fillers.mdl)$Task[,,2]
coef(dative_eykey.mdl)$Task[,,2]
coef(dative_hanthey.mdl)$Task[,,2]
coef(kwa.mdl)$Task[,,2]
coef(hago_lang.mdl)$Task[,,2]
coef(sinokorean.mdl)$Task[,,2]
coef(hisses.mdl)$Task[,,2]
```

## Posterior predictive checks

Plot all of them and save the resulting image file:

```{r, fig.width = 8, fig.height = 6}
for (i in seq_along(files)) {
  pp_check(get(files[i]), nsamples = 100)
  ggsave(str_c('../pp_check/', files[i], '.png'),
         width = 10, height = 6)
}
```

This completes this script.



